COG-ED Manuscript

### 2021-08-20 06_Paper/COG-ED/Manuscript.Rmd
completed all analysis code except for MLM

  data_hyp3 <- data.frame(subject = character(), auc = double())

@@

    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
                         auc = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = FALSE))
    data_hyp3 <- rbind(data_hyp3, newdata)

@@

  hypothesis3a <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc))

@@

# per participant, calculate one AUC for each NTLX subscale, then average the AUC within each participant
# predictor 1 is NTLX-AUC, predictor 2 is SV-AUC
# multiple regression to predict NFC
```

@@

# repeat H3b analysis with only the effort NTLX subscale AUC, not the composite of all subscales
```

>>>>

  data_hyp3 <- data.frame(subject = character(), auc_sv = double())

@@

    newdata <- data.frame(subject = data_SV$subject[subjectindex[i]],
                          auc_sv = auc(data_SV$level[subjectindex[i]:(subjectindex[i+1]-1)], data_SV$sv[subjectindex[i]:(subjectindex[i+1]-1)],
                                   method = "trapezoid", sort = FALSE))
    data_hyp3 <- rbind(data_hyp3, newdata)

@@

  hypothesis3a <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc_sv))

@@

  subjectindex <- c(1,which(data_ntlx$subject != dplyr::lag(data_ntlx$subject)),nrow(data_ntlx))

  ntlx <- data.frame(subject = character(), auc_mental = double(), auc_physical = double(), auc_time = double(),
                          auc_performance = double(), auc_effort = double(), auc_frustration = double())

  # calculate AUCs per NTLX subscale per participant

    newdata <- data.frame(subject = data_ntlx$subject[subjectindex[i]],
                          auc_mental = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
                                           data_ntlx$mental[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
                          auc_physical = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
                                           data_ntlx$physical[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
                          auc_time = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
                                           data_ntlx$time[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
                          auc_performance = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
                                           data_ntlx$performance[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
                          auc_effort = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
                                           data_ntlx$effort[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE),
                          auc_frustration = auc(data_ntlx$level[subjectindex[i]:(subjectindex[i+1]-1)],
                                           data_ntlx$frustration[subjectindex[i]:(subjectindex[i+1]-1)], method = "trapezoid", sort = FALSE))
    ntlx <- rbind(ntlx, newdata)

  # add column containing the average of the NTLX subscale AUCs

  ntlx <- cbind(ntlx, auc_ntlx = rowMeans(ntlx[ ,grep("auc", colnames(ntlx))]))

  # merge data frames based on subject

  data_hyp3 <- merge(data_hyp3, ntlx)

  # delete temporary data frame

  remove(ntlx)

  # compute multiple linear regression to predict NCS based on SV AUC and NTLX AUC

  hypothesis3b <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc_sv + data_hyp3$auc_ntlx))

@@

  # compute multiple linear regression to predict NCS based on SV AUC, Effort AUC and Mental Load AUC

  hypothesis3c <- summary(lm(data_hyp3$nfc ~ data_hyp3$auc_sv + data_hyp3$auc_mental + data_hyp3$auc_effort))
